A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2019-12-06 0_reviewer_response.tex

\Que{Example question by reviewer}
\Ans{Example response}
\revise{Old text in manuscript}{New text in manuscript}
\todo{Comment for us internally (should be removed before this letter is sent).}
\commits{123commit-hash}

\section{Reviewer 1}
Overall, the paper proposes some novel frameworks which are meaningful to additive manufacturing. Therefore, I suggest it for publication once the following major comments are addressed.

\Que{
Could the authors provide a mathematical foundation for the relationship between the underfill/overfill areas and the allowed variation of bead width? I believe the proposed beading scheme can reduce the underfill/overfill areas somehow. But we still lack a mathematical theory to guide the design.
}

\todo{
I actually think this question is mostly related to DfAM. I think we should add something like the following to the manuscript:
}

\revise{}{
Suppose that under some criterion of manufacturability we have established that we can attain bead widths within the range $[w_\text{min}, w_\text{max}]$.
We can then conclude that in order for a model to be manufacturable its widths should be within the set of ranges $\bigcup_{i\in \mathcal{N}}([i w_\text{min},i w_\text{max}])$.
If $w_\text{min} = w_\text{max} = w^*$ this reduces to $\{w^*, 2w^*, 3w^* \dots\}$.
On the other hand we assume that $w_\text{max} > 2 w_\text{min}$ and so a model is manufacturable if the feature size is within $[w_\text{min}, \infty]$ everywhere.
%If for example $\nicefrac23 w_\text{min} < w_\text{max} < 2 w_\text{min}$, a manufacturable model should have widths in the ranges $\{[w_\text{min},w_\text{max}],[2 w_\text{min}, \infty]\}$

However, we propose no such binary criterion of manufacturability;
instead we assume that the manufacturability generally diminishes as the requested bead width variation widens.
By keeping the bead widths closer to the preferred bead width any reasonable measure of manufacturability is higher than for alternative methods.
}
\todo{Actually add this to the manuscript!}

@@

\stepcounter{question}

\subQue{
The authors should highlight their contributions compared to the existing approaches for generating toolpaths with adaptive width.
}
\Ans{
afs
}
\commits{66d006d91d406c0064ee1f4f1e4df85fc0821994}

\subQue{
From Fig. 1(b) and (c), we can see that the approach in Jin et al (2017) can fill the sharp right end, but the proposed approach can not. 
}
\Ans{
We now use the same minimal feature size in all approaches.
This is now handled by the \emph{widening} meta-scheme.
We have added a figure to show that functionality.
See also our response to 1.6.
}
\todo{add widening changes; explain how widening is used in generating the results}
\commits{a5ddf3a73e3df20e43f25eafb93e9ce3a1393b13, d3fe6c86ee887da0e33fefdc43a83d014bc6047b, 0ac1c930a7cd2d1d305da730c9d5db20f4a8ea3f, 9281d8ae7350539102be0ead7b2ffc611591d2b4, a88ccd3309aef1233ed00ce9f22b244fe64668f4}

@@

\todo{
Tim:
Any beading scheme can easily be modified to change the minimal feature width, simply by supplying that $q(d) = 0$ if $d < w_\text{min}$ and that $q(d) = 1$ if $w_\text{min} < d < w^*$

Tim: changed widening scheme to handle both minimal feature size and minimal bead width
@others: The new widening scheme figure now shows a bug in widening, perhaps we should only control the min feature size and leave out widening.

Note: our tests do compare beading schemes with different $w_\text{min}$.
? Should we redo the tests?
}

\subQue{
If there is no sharp corners exist, then the existing approaches such as Jin et al (2017) do not have to use bead widths of large variations. 
}
\Ans{
The wedge shape of Fig. 1 was chosen because it contains a wide range of feature sizes and is therefore representative for a wide range of models.
Nearly every model induces the full range of $[0.5w^*,1.8w^*]$ using the centered approach by Jin et. al. 2017 JMS,
because nearly all models have feature sizes which span any range $[iw^*,(i+1)w^*]$ for $i\in\mathcal{N}$.
See Fig. 17 in the paper of Jin et al for an example shape.
Only shapes without central regions (a circle) or shapes with central regions with an exact multiple of $w^*$ everywhere (a rectangle) don't require any variation in bead width, but that holds for any of the beading schemes.

Figure~\ref{no_corners} shows an example of a shape without sharp corners, and which also requires a large bead width variation when using the constant bead count approach by Ding et al.
}
\begin{figure} \centering
\includegraphics[width=.5\linewidth]{response_no_corners}
\caption{Example shape without sharp corners but with a large variation in feature size.}
\label{no_corners}
\end{figure}

@@

\Que{
How do the authors conduct path planning? Could the authors add a simple 2D geometry with multiple holes to explain the path planning process? As the proposed approach adds more disconnected toolpaths to minimize underfill areas, an improper path planning would significantly increase the fabrication time. 
}

\todo{
Show results on printing time

Mention that the path order is not optimized
}

\Que{
While the proposed approach can use adaptive bead width to minimize underfill and overfill areas, the generated toolpaths are disconnected compared to the traditional approaches. From my experience, a small overfill area does not have to lead to serious defects. But the disconnected filaments definitely have worse mechanical performances compared to the continuous ones. 
}
\todo{
Tim: count number of extrusion toolpaths

Tim: That might be true, but the microgaps near 3-way intersections are not fillable using overfilling; the plastic cannot creap into those cravices.
}

\Que{
Why the authors state the inward distributed beading scheme as new? Jin et al (2017) has proposed the strategy to add a toolpath with varying width along the center edges of the skeleton, and with unchanging width outside.
}
\todo{
Tim: we should change the text to stress that we distribute the discrepancy over several beads rather than always over one bead.
}

@@

\Que{
\label{fig1geometry}
In Fig.1, how to justify the proposed approach as different geometries are used? I believe if the authors use the same geometries as in Fig 1. (a) and (b), there would be also underfill areas using the proposed approach. 
}
\Ans{
There are two ways in which we can interpret this question, leading to two responses.
The question can be interpreted as saying that Fig a has a different geometry than b or c.
There is now a black outline to show that the shapes in Fig 1a, b and c are actually the same geometry, and the output is less confusing because we now use the same minimum feature size for b and c.

The question can also be interpreted as saying that one might use a different shape than the geometry in Fig 1.
We decided on this wedge shape because it shows how the techniques deal with a wide range of feature sizes;
the wedge shape can be read as a graph where we can read out the resulting beading for any local feature size.
}
\todo{redo tests with min feature size}
\commits{45853e8b30d93f60e9465cbb649e347f9cfc23b1, 53224c04ceff6c1b18a9eea6de8e7e33957b7797}

\Que{
Please double check the following sentences. ”Third, the extruded path should ...”(at the second paragraph of Section 2) ”This the downward phase...” (at the last paragraph of Section 3.5) 
}
\Ans{
Okay. Thanks.
}
\commits{eb2a5207c83dfe069d3ab3fc37bf2149b8a51964}

@@

\Que{
In Fig.4, the bead count should marked in another way. The ultra thick solid line conflicts with that for ”outline”. 
}
\Ans{
Note that the bead count is the number, not the arrow from the number.
The arrow is now a double thin line.
}
\commits{07df258c1fa618808ba9493384550021a03c83e1}

\Que{
What are the differences between the distributed and the inward scheme in Fig. 16(d) and (e)? Are they the same? 
}
\Ans{
We have adjusted the range of the inward distributed scheme to $N=2$ in order to generate a bigger difference between these images.
}
\commits{735762b1e7daf31ae4465bf288ef867ded7da095}

\Que{
In Fig. 17(b), where is the curve for the ”uniform” case?
}
\Ans{
We've added it back in.
Note that the width of the uniform case is \SI{0.4}{\milli\meter} \emph{everywhere}, so the curve is not really informative.
}
\commits{e5f3649455c73c8146e8d07cce13bc1e89d84cbb}

@@

\section{Reviewer 2}
The paper is generally well written with clear illustrations. 
\Que{
There are occasional omissions, perhaps unintentional, such as the definition of a skeleton - see section 3.1, second paragraph. 
}
\Ans{
Indeed we have intentionally not defined the term `skeleton'.
It seems that there is no generally accepted \emph{intuitive} definition of `skeleton';
the first occurance of the term was as synonymous with the medial axis and it was only defined \emph{mathematically}.
However, the term is now used as an umbrella term for the various different types of skeleton.
We have changes the wording a bit to make clear that `skeleton' refers to an undefined umbrella term.
}
\commits{5356492b5a9a690228ffdb6a6a26cf10d099a7d4}

\stepcounter{question}
\subQue{
The authors seem to use linear approximations of the medial axis - see Figure 2 (b), which is understandable given the fact that they compute the MA with the Boost library. If this is so, can the authors comment on the implications of this approximation?
}
\Ans{
We chose for linear approximations because they simplify the process,
whereas we chose for Boost because it seemed more stable than alternative libraries.

The discretization is handled in section 3.2. Skeletal trapezoidation, second paragraph.
The discretization simplifies the algorithm, potentially at a slight computational cost.
Because we used $d^\text{discretization} = \SI{0.2}{\milli\meter}$, we can expect the discretized skeleton to deviate from the real skeleton by approximately \SI{0.013}{\milli\meter}, which is within the range of accuracy of the hardware system used.
The computation of this value is complicated by the fact that the discretization always introduces a sample point at the apex and at the boundaries of significant portions of the parabola.
(See section 3.3 Significance measure, last paragraph.)
See Figure~\ref{response_parabola_discretization}.

We don't feel this type of discretization error is worth extending the manuscript with.
}
\begin{figure}\centering
\includegraphics[width=.3\linewidth]{response_parabola_discretization}
\caption{Parabola discretization.
Thick black is part of the outline.
Red is significant skeleton, violet is non-significant skeleton.
}\label{response_parabola_discretization}
\end{figure}

\subQue{
For example, what happens if the obtuse outside angle in Figure 2 goes to 0? 
}
\Ans{
That figure is reproduced here in Fig.~\ref{overview_outline}.
As the rightmost two points move right the degree of the corner in the middle goes to zero which causes the parts of the parabola revealed are more accurately described by the discretization than the highly curved part in the middle.
}
\begin{figure}\centering
\includegraphics[width=.3\linewidth,rotate=-90]{response_simple_example_1}
\includegraphics[width=.3\linewidth,rotate=-90]{response_simple_example_2}
\includegraphics[width=.3\linewidth,rotate=-90]{response_simple_example_3}
\caption{Skeletal trapezoidation}\label{overview_outline}
\end{figure}

@@

\Que{
It would be nice to discuss why contour-parallel toolpaths are needed or selected. In what situations, these are required as opposed to zigzag style (or direction-parallel as referred in the text) patterns. Without such a discussion, the motivation seems a little weak. In the second paragraph of introduction, there is a short discussion about this but it sounds like the authors assume that even the perimeters (or outline) are printed with direction-parallel extrusion. However, common approach in FDM is to print the perimeters with contour parallel toolpaths and fill the inner region with direction-parallel paths only (as later acknowledged in the related work 3rd paragraph). I think the motivation for contour parallel toolpaths needs to be justified further. 
}
\Ans{
The industry standard is to use a combination of contour-parallel and direction-parallel.
We now clarify why contour-parallel is (partly) used and that in as much as contour-parallel is used, our approach improves on the industry standard.
}
\todo{
Add some sentences to make it clear

Show LimitedBeadingStrategy or StrategyType::OutlineAccuracy

explain this paper can be used in normal slicing
}

\commits{6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae, ac800628951417dcb28bd6e3a0ed08801735acf4, a88ccd3309aef1233ed00ce9f22b244fe64668f4}

### 2019-12-06 5_generalization.tex
redo (inward) distributed comparison fig (reviewer 1.9)

\begin{figure}
\centering
\setlength{\figwidth}{.4\columnwidth}
\setlength{\figheight}{.25\columnwidth}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight,frame]{sources-validation-wedge-Distributed-pretty-evenly.png}
\caption{Evenly distributed}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight,frame]{sources-validation-wedge-Distributed-pretty-inward.png}
\caption{Inward distributed}
\end{subfigure}
\begin{subfigure}[t]{.1\columnwidth}\centering
\includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}
\end{subfigure}
\caption{
Closeup of toolpaths generated with the distributed beading schemes for a large wedge shape.
Colors represent bead widths.
}
\label{distributed_comparison}
\end{figure}

>>>>

\begin{figure}
\centering
\setlength{\figwidth}{.8\columnwidth}
\setlength{\figheight}{.3\columnwidth}
\begin{minipage}[b]{0.8\linewidth}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[width=\figwidth]{sources-validation-wedge-Distributed-pretty-evenly.png}
\caption{Evenly distributed}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[width=\figwidth]{sources-validation-wedge-Distributed-pretty-inward.png}
\caption{Inward distributed}
\end{subfigure}
\end{minipage}
\begin{subfigure}[t]{.1\columnwidth}\centering
\includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}
\end{subfigure}
\caption{
Closeup of toolpaths generated with the distributed \revise{}{and inward ($N=1.5$)} beading schemes for a large wedge shape.
Colors represent bead widths.
}
\label{distributed_comparison}
\end{figure}
